TODO: A Survey of StarCraft AI Techniques

### 2013-02-14 survey.tex
Add iCCup ranking in intro, and start II.B.3 spatial and temporal reasoning

{\color{red} A typical Starcraft map is defined as a rectangular grid, typically ranging between 64x64 to 128x128 in size (although the resolution at which units move is finer), and each player can control up to 200 units (not including buildings). Moreover, each different race contains between 30 to 35 different types of units and buildings, each one with a significant number of special abilities}. All these factors together make Starcraft a significant challenge, in which humans are still much better than computers.

@@

\subsubsection{Spatial and Temporal Reasoning}
TODO just a paragraph on exposing why there are temporal and spatial reasoning in RTS AI.

>>>>

{\color{red} A typical Starcraft map is defined as a rectangular grid,
  typically  ranging between 64x64  to 128x128  in size  (although the
  resolution  at which  units  move  is finer),  and  each player  can
  control up  to 200 units (not including  buildings).  Moreover, each
  different race  contains between 30  to 35 different types  of units
  and  buildings,  each  one  with  a significant  number  of  special
  abilities}. All these factors  together make Starcraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. Indeed, best Starcraft AIs are ranked between $D$ and $D^-$
on the iCCup\footnote{http://www.iccup.com/starcraft/} ranking system,
where average  amateur players are  ranked between $C^+$ and  $B$. For
comparison, Starcraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial  reasoning   is  related  to   each  aspect  of   the  terrain
exploitation.  This  involves  buildings  placing  where  one  has  to
carefully  consider buildings  position  into its  own  bases to  both
protect them  by creating  a wall against  invasions and to  avoid bad
configurations  where large  units could  be stuck.  Base expansion
also belongs  to spatial reasoning,  in the sense  that the AI  has to
choose good available emplacements to  build a new base, regarding its
own  position  and opponent's  bases.  Finally,  spatial reasoning  is
closely related to  tactics with questions like ``Where  should I place
my  units for battle?'',  favoring for  instance engagements  when the
opponent's units are into a  bottleneck. In Starcraft, it is always an
advantage to  have its units  on high ground  whereas enemy is  on low
ground, since units  on low ground have no vision  on high ground, and
firing from low  ground have only 70\% of chance to  hit units on high
ground.

As well as spatial reasoning, temporal reasoning is related to tactics
since it implies  to decide about army movements,  like when attacking
or withdrawing  units from battle.  Strategy also copes  with temporal
reasoning, mainly  with planning problems:  when researching upgrades,
when constructing wished buildings,  when switching strategy if needed,
etc.
